Anisotropic in-plane thermal conductivity observed in multilayer silicene

### 2017-12-07 latex/paper.tex
合并郭志新的修改结果

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-11-22 12:00:25
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of Boltzmann Transportation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene. It is found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in interlayer direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicene with different reconstruction can reach up to $57.9 W/mK$, and can be as low as $3.31 W/mK$ and the anisotropy can be as high as $41.1\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction decreases significantly, but the thermal conductivity increases a little in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection of surface reconstruction. Phonon lifetime and group velocity play differenct roles in bilayer structures and 3-8 layer structures where the anisotropy of the former is mainly effected by the anisotropy of lifetime but that of the later is the result of anisotropy of group velocity.  This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicene, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

Many theorical experiment result has shown that quantum confinement and surface effects could reduce thermal conductivity remarkably while remain the electric conductivity remain at a relatively high level, which made them potential in the application of thermalelectric field where the thermalelectric figure of merit $ZT=\frac{S^2 \sigma T}{\kappa}$ could be optimized by the reduced thermal condutvitiy. For example the experiment of Boukai et.al.\cite{Boukai2008} shows that by varying the nanowire size and impurity doping levels, ZT values representing an approximately 100-fold improvement over bulk Si are achieved over a broad temperature range. And Hochbaum et.al.\cite{Hochbaum2008} proposed a way of enchancing thermalelectric effieciency by control the roughness of silicene nanowires.At present, research of thermal transport properties based on the silicene nano structure mainly includes silicene nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008}, silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014}, substrate supported silicene\cite{Wang2015,Zhang2015a}, silicene thin film and bulk structure\cite{Bodapati2006,Tang2013Thermal,Jeong2012Thermal,Liu2006Thermal,Wang2006Lattice}. Due to the quantum size effect in the thickness direction and surface reconstruction effect, silicene multilayer structure is expected to have lower thermal conductivity than the bulk and is more suitable for thermoelectric applications. However, the study on the properties of multilayer silicene thermal transport is still very rare.

The existing research about the thermaleletric properties of low-dimensional materials focused on the range of  two-dimensional mateirals with interlayer interaction of  Van der Waals(vdW) type and there is no surface reconstruction. There have been lots of studies on the electronic and thermal transport properties for this kind of typical layered structure and hetero structures, such as graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, black phosphorus\cite{Zhang2015,Peng2015,Jain2015} two-dimensional layered structure. The existing preparation technology such as mechanical stripping, molecular beam epitaxy has difficult to produce nano layered structure for the material with strong interaction between layers, and the research of this kind of super thin nano materials has been very scarce. Recently, it has been found that monolayer and multilayer silicene material can be grown on some metal substrates by molecular beam epitaxy\cite{Fleurence2012,Meng2013,Vogt2012,DePadova2013,Feng2012}. The progress of these experiments ignited the upsurge the two dimensional nanomaterials with strong interaction between layers. In contrast to vdW, the two layer nano materials, which are represented by multi-layer silicene, exhibit special surface reconstructions which are different from the bulk surface\cite{Fleurence2012,Meng2013,Feng2012,Guo2013} and its physical and chemical properties are also very unique\cite{Guo2013,Guo2015}, indicating that there is new physics in this kind of ultra-thin nano materials. The study of these of covalent type are relatively rare which may provide a possibitity of high effiency thermaleletric 2D mateirials.Previous studies have shown the big difference of electronic properties in low dimensional phases and build phases. In the case of silicene, the surface reconstruction could be a significant factor which determines wheather it's metal or semiconductor \cite{Guo2015Structural}. And it's expected that the complicated surface reconstruction affects thermal transportation quite a lot, especially it's possible to obtain novel structures with ultralow or highly anistropic thermal conducitivity by changing surface recontruction. This could help reveal a general rule between thermal transportation properties and low-dimensional structures and may promote the application of covalente bonded multilayer 2D materials in the thermaleletricity field.

In this work we use multilayer silicene as a group of  ideal model systems to explore the effects of layer number and  surface reconstruction charateristics on the intensity and anisotrope of the 2D dimentional materials.silicene  is currently the only one system, from its monolayer to multilayer, and then to the bulk structure, that have been prepared by experiment. And it has rich and typical structure in the dimension of zero dimension, one dimension and three dimensions, which have laid a very good foundation for the study of two-dimensional scale multilayer silicene. The study of multilayer silicene is also helpful to understand the physical evolution of matter from low dimension to high dimension. In addition, the preparation process of silicene nano materials is mature and the raw materials are rich, and It has a broad application prospect in the fields of micro nano electronics, energy, information and other important fields in the future. Based on the first principles calculation of Guo\cite{Guo2015Structural}, we explored the thermal transport properties of the 2 to 10 layer silicene structure.

@@

The thermal conductivity of multilayer silicene structures are studied with the Boltzmann transportation equation(BTE) method realized in ShengBTE\cite{Li2014}. In order to well simulate the structures of different phase by BTE as well as saving computing effort, the latest classical Mod potential\cite{Parks2007} based on the large scale parallel and efficient LAMMPS molecular dynamics software package is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicene material elastic constants, the melting point and phase transition.The Mod potential is constructed for different type of silicene structures by fitting its bond angle parameter to give correct melting point and elastic constants and is constructed referring the correction of the equilibrium bond length based on the experimental diamond structure and leads to smaller the binding energy than that predicted by the first principle method.

The model silicene structures are shown in FIG.\ref{fig:structures} which are picked from recent work of Guo et al\cite{Guo2015Structural}.For convenience, we define the names of these structures as "nlxs", where n is a pure number, representing the number of layers, l represents layer, x distinguishes different structures (concrete 1, 2, 3 etc. ) and s indicates the type along the length direction with value of a (armchair) or z (zigzag). TABLE.\ref{tab:table1} lists the structure name and  the minimum repeat cell periodicity of the multilayer silicene.

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/structures}
  \caption{\label{fig:structures}  (color online) Some typical structure of multilayer silicene. Within which  are top view and side view of the studied structures. The buckling atoms on the top surface are labeled as yellow while the red atoms represent the others on the top surface. All the atoms on the bottom surface are labeled as blue. The greens represent those that are inside the structure. The orientation of top view of the cells is labeled as arrows.}
\end{figure}

Before calculating thermal transportation properties, the  structures are  optimized with  conjugate gradient (CG) method which guarantee the stability of them .  Then finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thridorder respectively are applied to extract second- and third-order force constants (FCs) in which hundreds of  slightly displaced supercells are generated and their forces are calculated with LAMMPS and used to calculate the FCs with  numerical differential calculation. The chosen supercells is $3 \times 3 \times 1$ of premitive cells to make the inplane dimension above  $40\angstrom$ which make  forces acurrate enough. As for the out-of-plane dimension, according to the previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the thickness of each layer.

The thermal conductivity tensor could be calculated with

@@

Where $c_{k \sigma}$ means heat capacity of phonon mode $k \sigma$, $v^{\alpha}$ present for mode group velocity and $\tau_{k \sigma}$ is phonon lifetime. The heat capacity  could be computed with Eq.(\ref{eq:cv}) .

@@

Where $ f(\omega,T)=1/(exp(\frac{\hbar \omega}{k_b T})-1)$ is Bose-Einstein distribution function.

The calculations of $c_{k\sigma}$ , $v_{k\sigma,\alpha}$, and $\tau_{k\sigma}$ require second- and third-order force constants (FCs) as inputs and the detail formulas are refered to the work of  Wu Li\cite{Li2014}. To avoid underestimate of thermal concutivity,Iteration method is used instead of relaxation time approximision (RTA) .A $45\times 45 \times 1$ Monkhorst-Pack q-point mesh is used to obtain enough phonons for the convergence of the summation as well as for further statistical analysics of them.

@@

Surface reconstruction is found to have substantial influence on the intensity and anisotropy of thermal conductivity. The relationship between the thermal conductivity  and the length of three kinds of bilayer silicene along different directions is shown in FIG.\ref{fig:tc_length_sheng}(a). The absolute value of the thermal conductivity shows a large gap between these different surface reconstructions. The thermal conductivity of 2l1 structure reaches up to $42.1W/mK$ and $57.9W/mK$ in the zigzag and armchair directions respectively , while those of 2l2 structure are about $31.1W/mK$ in both direction and those of 2l3 structure are around $5W/mK$. 2l2 and 2l3 structures both show large anisotropy while 2l2 does not because 2l2 structure exhibits excellent rotation symmetry of $\frac{\pi}{2}$. The thermal conductivity and anisotropy of multilayer silicene is shown in TABLE.\ref{tab:table1}.   The above results show that surface reconstruction has a significant effect on the thermal transport properties of multilayer silicene. The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction. Meanwhile, the anisotropy of the surface structure leads to the significant anisotropy of the thermal conductivity.

The thermal conductivity converged with cutoff MFP very quickly in the curve of 2l2 while a little slower in the others. Besides, the cutoff MFP of 2l1 structure exhibits much difference in the two directions  which maybe due to the diffence of scattering intensity caused by the surface conditions.When the length of the silicene is smaller than the mean free path of the phonon, the ballistic transport properties of the phonon are obvious. When the length is larger than the mean free path of the phonon, the phonon scattering transport characteristics are obvious. The empirical formula of the John A. Thomas\cite{Thomas2010} can be used to characterize the thermal conductivity of the phonon transport from ballistic to scattering region, at the same time accurately obtaining thermal conductivity of the infinite long nano materials. Using this formula, we obtain the thermal conductivity of infinitely long multilayer silicene
\begin{equation}
  \kappa = \kappa_\infty (1-e^{-\frac{L}{L_c}}) \label{eq:eq_nemd}
\end{equation}

where $\kappa_\infty$ is the fitted full scattering thermal conductivity. $L_c$ is the transition length from the ballistic transportation to the scattering transportation.

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/tc_length_sheng}
  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene. b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.(\ref{eq:eq_nemd}). The letter z/a in the legend mean the transport direction is zigzag/armchair. The dots of 2l2a and 2l2z are almost the same so red solid dots are covered. }
\end{figure}

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/chi}{}
  \caption{\label{fig:chi} (color online) The anisotropy value dependence on length calculated with Eq.(\ref{eq:eq_chi})}
\end{figure}

With the increase of layer number the anisotropy decreases for layer number larger than three. Here we study mainly on multilayer silicene structure with 3-8 layers, whose  surface has typical Si (111) $2 \times 1$ surface reconstruction.   From TABLE.\ref{tab:table1}, for the stuctures with more than three layers,the thermal conductivity of the multilayer silicene with zigzag type is higher than that of armchair. $\kappa_z$ decreases while $\kappa_a$ increases. The reason is that the zigzag direction of the multilayer silicene surface is composed of a smooth zigzag atomic chain (as shown in FIG.\ref{fig:structures}). Compared with the bulk silicene structure, the heat conduction along the zigzag direction has no obvious effect on the heat flow. While along the armchair direction, the fluctuation of multilayer silicene surface is very large, the same is its obvious affection on heat flow. This difference is mainly caused by the surface reconstruction effect, and will decrease with the increase of the thickness of the silicene. It's expected that when the layer number reaches infinity the value of them collapse because we finally obtain the bulk phase. The value
\begin{equation}
  \chi=\frac{|\kappa_{z,\infty}-\kappa_{a,\infty} |}{ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) } \times 100 \%  \label{eq:eq_chi}
\end{equation}

is used to measure the thermal conductivity difference in different directions, where $ \kappa_{z,\infty} (\kappa_{a,\infty})$ stands for the full scattering thermal conductivity (infinite thermal conductivity) in the zigzag (armchair) direction. And is $ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) $ the maximum value of thermal conductivity in the two directions. The magnitude of the anisotropy $\chi$ is also shown in TABLE.\ref{tab:table1},which  decreases obviously for these structures which is expected. The case of three layers is exceptional whose values are much larger than the structures with those with larger layer number and possesses a smaller anisotropy. This could be understood by the direct interaction beteen the top and bottom sides , and also the absence of hexatomic ring in the side view compared with 4l1 structure.A deeper analysis of this of it could be found in work of Guo \cite{Guo2015Structural}.

On the other hand, the size effect of the thermal conductivity anisotropy is obvious in 2l1 but not in the others. As shown in FIG.\ref{fig:chi}, thermal conductivity in 2l1 is almost isotropic  in the case of short length (10 - 1000 $\angstrom$). When the length is above 1000  $\angstrom$), thermal conductivity become inceasingly anisotropic. This is essentially due to the difference acoustic branch along different directions whose mean free path are rather large, which is caused by phonon scattering of umklapp process. However, for 3-8 layer structures, thermal conductivity is highly even in the short free path region which indicates anistropy in both low and high frequency range and this could  be verified in the following contents. The anisotropy in 2l3 is somelike the mixture of both mechanism but has also a pretty large contribution from long path phonons.

\begin{table*}
  \caption{\label{tab:table1}
    The thermal conductivity and anisotropic ratio of different multi-layer silicene.Along with the average heat capacity ($kJ/m^3/K$) of zigzag direction and armchair direction.}
  \begin{ruledtabular}
    \begin{tabular}{ccccccc}
          & Minimal period
          & $\kappa_{z,\infty}$
          & $\kappa_{a,\infty}$
          & $\chi$
          & $Cv_{z}$
          & $Cv_{a}$                                                           \\
      \hline
      2l1 & $1 \times 1$             & 42.10 & 57.92 & 27.31\% & 165.8 & 166.7 \\
      2l2 & $\sqrt{2}\times\sqrt{2}$ & 31.11 & 31.11 & 0    \% & 38.44 & 38.44 \\
      2l3 & $2 \times 2$             & 3.311 & 5.624 & 41.13\% & 22.42 & 22.42 \\
      3l1 & $2 \times 1$             & 31.44 & 14.05 & 55.29\% & 52.22 & 52.46 \\
      4l1 & $2 \times 1$             & 20.37 & 6.114 & 69.98\% & 37.71 & 37.89 \\
      5l1 & $2 \times 1$             & 19.33 & 6.419 & 66.78\% & 29.17 & 29.32 \\
      6l1 & $2 \times 1$             & 17.78 & 6.527 & 63.29\% & 23.73 & 23.86 \\
      8l1 & $2 \times 1$             & 17.56 & 7.461 & 57.51\% & 17.26 & 17.36 \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}

For the structures of two layers the anisotropy mainly comes from low frequency phonons while that of layer number more than fore are contributed from high frequency phonons. The frequency distribution of thermal conductivity is shown in Fig.\ref{fig:tc_freq} and it's obvious that both 2l1 and 2l3 have much larger value in the low frequency part of armchair direction and they are the only two structures with thermal conductivity of armchair direction larger than that of zigzag direction. For the other structures except 3l1, the low frequency region exhibits little anisotropy while the high frequency thermal condcutivity of zigzag contribution is larger than that of armchair direction. Besides, the curves show much similarity for 4l1,5l1 and 6l1, suggesting a common mechanism of the anisotropy of them.

To have a deeper inside into the origin of anisotropy for all the structures it's helpful to study all the factors that contribute to thermal conductivity according to Eq.(\ref{eq:kappasum}).

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-11-22 14:17:59

\documentclass[aps,prb,twocolumn,showpacs,amsmath,amssymb]{revtex4-1}

\preprint{APS/123-QED}

\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math

\usepackage{multirow}
\usepackage{epsfig}
\usepackage{amssymb}

\newcommand{\angstrom}{\mbox{\normalfont\AA}}

\begin{document}

\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Zhi-Xin Guo${}^{2,1}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
The silicon materials present complex surface reconstructions, which are usually neglected for the thermal conductivity investigations due to their small specific surface area. However, the reconstruction effect can be significant when the material thickness becomes ultra thin, i. e., multilayer silicene. Here we systematically study the thermal conductivity of multilayer silicene by means of Boltzmann Transportation Equation (BTE) method.  We find that the thermal conductivity of multilayer silicene present significant surface-structure dependence. The thermal conductivity of bilayer silicene varies from $3.31$ W/mK to $57.9$ W/mK depending on the specific surface structures. We also find that the surface reconstruction induces unusual large thermal conductivity anisotropy, which reaches 70\%  for the flour-layer  $2\times1$ silicene.  The anisotropy decreases with silicene thickness increasing, owing to the significant reduction of the thermal conductivity in the zigzag direction and its slight increment  in the armchair direction. 
Finally, we find that both the phonon-lifetime  anisotropy and the phonon-group-velocity  anisotropy contribute to the thermal conductivity anisotropy for the multilayer silicene.
This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nanomaterials  with surface constructions in the future.

  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicene, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

Many theoretical and experimental results have shown that quantum confinement and surface effects could reduce thermal conductivity remarkably while remain the electric conductivity remain at a relatively high level, which made them great potential in the applications of thermoelectrics. For example, the experiment of Boukai \emph{et al}.\cite{Boukai2008} shows that by varying the nanowire size and impurity doping levels, ZT values of approximately 100-fold improvement over bulk Si are achieved over a broad temperature range. Hochbaum \emph{et al}.\cite{Hochbaum2008} also proposed a way of increasing ZT by controling the roughness of silicene nanowires. At present, the thermal conductivity of the silicon nanostructures, i. e.,  silicene nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008} and monolayer silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014,Wang2015,Zhang2015a} \textbf{Add, J. Phys.: Condensed Matter 28, 145003 (2016)} had been well studied. However, the thermal conductivity of multilayer silicene is still mysterious.  
The combined effects of quantum size and surface reconstruction in multilayer silicene is expected to induce exotic thermal transport properties different from both monolayer silicene and bulk Si,  which may make it suitable for the thermoelectric applications. Since the the thermal conductivity of monolayer silicene and  bulk Si have been well explored, investigation on multilayer silicene is also helpful for understanding the thermal conductivity  evolution from two dimensional (2D) to three dimensional (3D) systems.

The existing research on thermal conductivity of  2D materials  mainly focus on the ones with weak Van der Waals(vdW) interlayer interaction where there is no surface reconstruction, such as multilayer graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, and black phosphorus\cite{Zhang2015,Peng2015,Jain2015}.  Whereas, the thermal conductivity of 2D materials with strong interlayer interactions have been barely explored.
The multilayer silicene which has been both theoretically predicted and experimentally synthesized can be an ideal material for such an investigation\cite{}\textbf{ [add more refs on mutilayer silicene, such as Appl. Phys. Lett. 102, 163106 (2013); Appl. Phys. Lett. 104, 131904 (2014),Guo2015Structural}. 
Previous studies  showed that the mutilayer silicene exhibit special surface reconstructions which induces the intriging electronic properties ( \textbf{ Ref. Appl. Phys. Lett. 104, 131904 (2014), Guo2015Structural}. Naturally, one can expect that  the surface reconstruction is a significant factor for the thermal conductivity. 
Especially, revealing the surface reconstruction effect on thermal conductivity anisotropy  in mutilayer silicene  promotes the applications of covalently bonded 2D materials in the thermoelectrics.

In this work, we systematically study the in-plane thermal conductivity of multilayer silicene with various thickness  (2-10 atomic layers) and surface reconstructions in use of  the BTE method.  We find that the thermal conductivity of multilayer silicene is significantly affected by the surface reconstructions, which can induce  either ultralow thermal conductivity value ($3.3$ W/mK) or unusual high thermal conductivity anisotropy (70\%).  This feature shows that the  multilayer silicene is an ideal candidate in the thermoelectrics.

@@

The thermal conductivity of multilayer silicene structures are studied with the BTE method realized in ShengBTE\cite{Li2014}. In order to save the computing expense, the latest classical Mod potential\cite{Parks2007} based on the large scale parallel and efficient LAMMPS molecular dynamics software package is chosen\cite{Kumagai2007Development}. This potential is able to reconstruct the silicene material elastic constants, the melting point and phase transition. The Mod potential is constructed for different type of silicene structures by fitting its bond angle parameter to give correct melting point and elastic constants and is constructed referring the correction of the equilibrium bond length based on the experimental diamond structure and leads to smaller binding energy than that predicted by the first principle method.

The atomic models for multilayer silicene are shown in FIG.\ref{fig:structures}, which are adoped from recent work of Guo \emph{et al}\cite{Guo2015Structural}. For convenience, we define the names of these structures as "nlxs", where "n" is a pure number, representing the number of layers, "l" represents layer, "x" distinguishes different structures (concrete 1, 2, 3 etc. ) and "s" indicates the type along the length direction which is a (armchair) or z (zigzag). We show in TABLE.\ref{tab:table1} the structure names and  the minimum repeat cell periodicities of the multilayer silicene.

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.95\linewidth]{structures.eps}
  \caption{\label{fig:structures}  (color online) Some typical structure of multilayer silicene. Within which  are top view and side view of the studied structures. The buckling atoms on the top surface are labeled as yellow while the red atoms represent the others on the top surface. All the atoms on the bottom surface are labeled as blue. The greens represent those that are inside the structure. The orientation of top view of the cells is labeled as arrows.}
\end{figure}

Before thermal conductivity calculation, the  structures are fully optimized using the conjugate gradient (CG) method to make them stable.  Then finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thridorder respectively are applied to extract the second- and third-order force constants (FCs), in which hundreds of  slightly displaced supercells are generated. The obtained forces are calculated and used to calculate the FCs with numerical differential calculation. The chosen supercells are $3 \times 3 \times 1$ of premitive cells to make the in-plane dimension above 40 \angstrom, which ensures  the accuracy of calculated forces. Following to previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the interlayer thickness.

The thermal conductivity tensor can be calculated as

@@

where $c_{k \sigma}$ means the heat capacity of phonon mode,  $v_{k \sigma}^{\alpha}$ represents the mode group velocity, and $\tau_{k \sigma}$ is the phonon lifetime. The heat capacity is calculated with Eq.(\ref{eq:cv})

@@

where $ f(\omega,T)=1/(exp(\frac{\hbar \omega}{k_b T})-1)$ is Bose-Einstein distribution function.

The calculations of $c_{k\sigma}$ , $v_{k \sigma}^{\alpha}$, and $\tau_{k\sigma}$ require the second- and third-order force constants (FCs) as inputs, where the detailed formulas are referred to the work of  Li \cite{Li2014}. To avoid underestimation of thermal conductivity, iteration method is used instead of relaxation time approximation (RTA). A $45\times 45 \times 1$ Monkhorst-Pack q-point mesh is used to obtain enough phonons for the convergence on the summation, as well as for their further statistical analytics.

@@

We first show that the surface reconstruction has substantial influence on thermal conductivity of the multilayer silicene. 
FIG.\ref{fig:tc_length_sheng}(a) presents the length dependence of thermal conductivity of three bilayer silicene structures. 
As one can see, thermal conductivity converges with cutoff phonon mean free path (MFP) very quickly in of 2l2  structure, while a little slower in the others. Moreover, the cutoff MFPs of 2l1 structure are very different in the armchair and zigzag directions. These features can be attributed to the different scattering intensity caused by the surface reconstructions.  
It is known that the ballistic phonon transport is dominating  when a material length the is smaller than the MFP,  whereas the diffuse phonon transport is  dominating when a material length is larger than the MFP.  
An empirical formula had been proposed by John A. Thomas\cite{Thomas2010}  to characterize the thermal conductivity of the phonon transport from ballistic to diffuse region, and accurately estimate thermal conductivity of the infinite long nanomaterials

\begin{equation}
  \kappa = \kappa_\infty (1-e^{-\frac{L}{L_c}}) \label{eq:eq_nemd}
\end{equation}

where $\kappa_\infty$ is the fitted full scattering thermal conductivity, $L_c$ is the transition length from the ballistic transportation to the diffuse transportation. Here we find that the length dependence of thermal conductivity of multilayer silicene can also be well described by this  formula.
The saturated thermal conductivity of 2l1 structure reaches up to 42.1 (57.9) W/mK in zigzag (armchair) direction, while it is  31.1 (31.1) W/mK  for 2l2 structure and  3.3 (5.6)  W/mK for 2l3 structure in zigzag (armchair) direction, confirming the significant influence of surface reconstruction on thermal conductivity.

The surface reconstruction also induces the thermal conductivity anisotropy, which can be estimated using 
\begin{equation}
  \chi=\frac{|\kappa_{z,\infty}-\kappa_{a,\infty} |}{ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) } \times 100 \%  \label{eq:eq_chi}
\end{equation}
where $ \kappa_{z,\infty} (\kappa_{a,\infty})$ stands for the full scattering thermal conductivity (infinite thermal conductivity) in the zigzag (armchair) direction. 
It is found that both 2l2 and 2l3 structures show large thermal conductivity anisotropy, i.e., 27\% and 41\%, respectively, while 2l2 structure does not exhibits the anisotropy owning to its rotational symmetry over $\pi/2$.  The ultra low and perticularly high anisotropy of thermal conductivity of bilayer silicene indicate its great potential applications in the thermoelectrics.

\begin{figure}[b]
 \includegraphics[angle= 0, width=0.9\linewidth]{tc_length_sheng.eps}
  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene. b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.(\ref{eq:eq_nemd}). The letter z/a in the legend mean the transport direction is zigzag/armchair. The dots of 2l2a and 2l2z are almost the same so red solid dots are covered. }
\end{figure}

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.9\linewidth]{chi.eps}{}
  \caption{\label{fig:chi} (color online) The anisotropy value dependence on length calculated with Eq.(\ref{eq:eq_chi})}
  \end{figure}

We then discuss the thickness dependence of the thermal conductivity anisotropy. Here we mainly focus on the multilayer silicene with 3-8 atomic layers, whose surface presents the typical $2 \times 1$ Si(111) reconstruction.   A common feature is that the thermal conductivity in the zigzag direction ($\kappa_z$) is obviously  higher than that  in armchair ($\kappa_a$) direction, which induces anisotropy larger than 55\%. 
The reason is that the zigzag direction of surface is composed of smooth zigzag atomic chains (as shown in FIG.\ref{fig:structures}), which are favorable for the heat transport. Whereas,  there are large geometry fluctuations in the armchair direction of the surface, which are unfavorable for the heat transport. 
With the silicene thickness increasing from 4 to 8 atomic layers, the anisotropy monotonically decreases from 70\% to 58\%, showing the negative  effect of thickness on  thermal conductivity anisotropy. The negative  effect  is attributed to the decrease of $\kappa_z$ and increase of $\kappa_a$  with the  thickness increasing. 
%This feature partially explains why the thermal conductivity  is almost isotropic in bulk Si, which usually has complex surface reconstructions. 
One exception is for the trilayer silicene, which has the largest thermal conductivity  but the smallest  anisotropy, compared to the thicker  $2\times1$ structures.  This could be understood by the direct interaction between the top and bottom layers, as well as the absence of ideal honeycomb ring under the surface layers, which is different from the thicker $2\times 1$ structures\cite{Guo2015Structural}.

We also investigated the size effect on the thermal conductivity anisotropy. As shown in FIG.\ref{fig:chi}, thermal conductivity of  2l1 bilayer silicene is almost isotropic  with length being 10-1000 \angstrom, and it becomes increasingly anisotropic with the length increasing  above 1000  \angstrom. This is essentially due to the difference of acoustic phonons in different directions,  which have large MFP.  As for the $2\times1$ structures with 3-8 Si layers in thickness, the high thermal conductivity anisotropy is obtained even when the length is as short as 10 \angstrom, implying that the anisotropy is  mainly attributed to the optical phonons. On the other hand, the thermal conductivity anisotropy of 2l3 silicene can be owning to both acoustic and  optical phonons in different directions.

\begin{table*}
  \caption{\label{tab:table1}
    The thermal conductivity and anisotropic ratio of different multi-layer silicene. Along with the average heat capacity ($kJ/m^3/K$) of zigzag direction and armchair direction. $Cv_z$ and $Cv_a$ correspond to the  heat capacity for thermal conductivity in  zigzag and armchair directions, respectively. }
  \begin{ruledtabular}
    \begin{tabular}{ccccccc}
          & Minimal period
          & $\kappa_{z,\infty}$
          & $\kappa_{a,\infty}$
          & $\chi$
          & $Cv_{z}$
          & $Cv_{a}$                                                           \\
      \hline
      2l1 & $1 \times 1$             & 42.10 & 57.92 & 27.31\% & 165.8 & 166.7 \\
      2l2 & $\sqrt{2}\times\sqrt{2}$ & 31.11 & 31.11 & 0    \% & 38.44 & 38.44 \\
      2l3 & $2 \times 2$             & 3.311 & 5.624 & 41.13\% & 22.42 & 22.42 \\
      3l1 & $2 \times 1$             & 31.44 & 14.05 & 55.29\% & 52.22 & 52.46 \\
      4l1 & $2 \times 1$             & 20.37 & 6.114 & 69.98\% & 37.71 & 37.89 \\
      5l1 & $2 \times 1$             & 19.33 & 6.419 & 66.78\% & 29.17 & 29.32 \\
      6l1 & $2 \times 1$             & 17.78 & 6.527 & 63.29\% & 23.73 & 23.86 \\
      8l1 & $2 \times 1$             & 17.56 & 7.461 & 57.51\% & 17.26 & 17.36 \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}

To explore the origin of anisotropy, we have calculated the frequency distribution of thermal conductivity in armchair and zigzag directions  (Fig.\ref{fig:tc_freq}).
It is found that the  anisotropy is mainly attributed to the low-frequency (0-5 THz) phonons for the bilayer silicene, i. e., 2l1 and 2l3, where thermal conductivity in armchair direction is obviously larger than that of zigzag direction.
Whereas, for the $2\times1$ structures thicker than 3 Si layers, the thermal conductivity in armchair and zigzag directions is nearly the same in the low-frequency region, and the anisotropy is mainly  attributed to the high-frequency (5-20 THz) phonons. 
In addition, the anisotropy of the 3l1 structure is resulted by the  phonons with frequency in range of 10-20 THz, below which the summation of contributions to thermal conductivity are nearly the same in armchair and zigzag directions.

To have a deep inside into the origin of anisotropy, it's helpful to investigate all the factors that contribute to thermal conductivity according to Eq.(\ref{eq:kappasum}).
We selected all the phonons along  $\Gamma\rightarrow X$ and $\Gamma \rightarrow Y$ directions in BZ, and calculated their heat capacity with Eq.(\ref{eq:cv}). The averaged heat capacity of silicene structures are shown in Table.\ref{tab:table1}, where $Cv_z$ and $Cv_a$ correspond to the  heat capacity for thermal conductivity in  zigzag and armchair directions, respectively.  As one can see, $Cv_z$ and $Cv_a$  strongly depend on the reconstruction-structure and thicknes of multilayer silicene, but their difference in the same structure is very small. This result shows that the thermal conductivity anisotropy is insensitive to the heat capacity. 
%This is due to the insensitivity of heat capacity to frequency when the frequency is low and the value is ignorable when frequency is relatively high, which means when considering only acoustic phonons the heat capacity is close to constant.

\begin{figure}[b]
  \includegraphics[width=0.9\linewidth]{tc_freq.eps}
  \caption{\label{fig:tc_freq} (color online)  The converged thermal conductivity versus phonon frequency of the structures. }
\end{figure}

\begin{figure}[b]
  \includegraphics[width=0.9\linewidth]{tau.eps}
  \caption{\label{fig:tau} (color online) Lifetime of phonons considering three-phonon scattering for all the structures. }
\end{figure}
